Supplementary Information for\\ ``A weakly structured stem for human origins in Africa''

### 2023-03-14 supplement.tex
simon comments in supp

With up to six sampled populations in final demographic models that we fit,
there are many parameters to learn. Even in the simplest model involving all
populations (such as the tree-like single-origin model), there are a few dozen
parameters defining split times, migration rates, admixture timings and
proportions, and population sizes and size changes. Thus, parameter space for a
given model topology is large. In addition, the space of possible model
topologies is itself large – as the number of populations increases, the number
of possible topologies also increases, as there are more possibilities for the
order of divergence and admixture events.

@@

Our models also included recent events to account for known migrations,
admixtures, and growths and declines in effective population sizes. Many of
these parameters were fixed based on previous historical, genetic, or
anthropological research, namely
\begin{itemize}
    \item Western African vs. eastern African divergence: 60ka
        \citep{Pagani2015-pz,Chevrier2018-vv,Niang2020-xt}
    \item Eastern Africa vs. British divergence (i.e., OOA): 50ka
        \citep{Mellars2011-sr,Fu2014-am,Hublin2020-nk}
    \item Neanderthal introgression to Eurasian branch: 45ka \citep{Reilly2022-ym}
    \item Mende population expansion: 5ka \citep{Tennessen2012-oy}
    \item Gumuz population decline: 5ka
    %We actually don't have a citation for this. Leaving blank. 
    \item East African pastoralist to South African admixture: 2ka \citep{Henn2008-xo}
    \item European to South African admixture: 10 generations ago \citep{Uren2016-nn}
    \item South African population decline following colonial admixture: 9 generations ago \citep{Van_Eeden2022-od}
\end{itemize}
The total number of parameters that were ultimately inferred were 21-31, depending on the complexity
of the model.

>>>>

With up to six sampled populations in final demographic models that we fit,
there are many parameters to learn. Even in the simplest model involving all
populations (such as the tree-like single-origin model), there are a few dozen
parameters defining split times, migration rates, admixture timings and
proportions, and population sizes and size changes. Thus, parameter space for a
given model topology is large. In addition, as the number of populations
increases, the number of possible topologies also increases, as there are more
possibilities for the order of divergence and admixture events.

@@

Our models also included recent events to account for known migrations,
admixtures, and growths and declines in effective population sizes. Many of
these parameters were fixed based on previous historical, genetic, or
anthropological research, namely
\begin{itemize}
    \item Western African vs. eastern African divergence: 60ka
        \citep{Pagani2015-pz,Chevrier2018-vv,Niang2020-xt}
    \item Eastern Africa vs. British divergence (i.e., OOA): 50ka
        \citep{Mellars2011-sr,Fu2014-am,Hublin2020-nk}
    \item Neanderthal introgression to Eurasian branch: 45ka \citep{Reilly2022-ym}
    \item Mende population expansion: 5ka \citep{Tennessen2012-oy}
    \item Gumuz population decline: 5ka \citep{Gopalan2022-pw}
    \item East African pastoralist to South African admixture: 2ka \citep{Henn2008-xo}
    \item European to South African admixture: 10 generations ago \citep{Uren2016-nn}
    \item South African population decline following colonial admixture: 9 generations ago \citep{Van_Eeden2022-od}
\end{itemize}
The total number of parameters that were ultimately inferred were twenty-one to
thirty-one, depending on the complexity of the model.
